A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-06 paper.tex

\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{float}
\usepackage{tabularx}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic,algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\graphicspath{{./images/}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

% alternative solution => IPFS(data) + MAM(index)
\subsection{Digital Identity}
The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions. We select the decentralized identity model rather than a centralized one for the concerns in Table.\ref{tab:did}.

\begin{table}[h]
	\caption{The comparism of centralized and decentralized identity model}
	\label{tab:did}
	\begin{tabularx}{\linewidth}{|l|X|X|}
	\hline
		\textbf{Identity Model} & \textbf{Centralized} & \textbf{Decentralized} \\
		\hline
		Control & Enterprises control identities & Entities control their identities \\ 
		\hline
		Security & Identity holded in a centralized service is a honeypot for cyber attacks & Decentralized identity limits data exposure \\ 
		\hline
		Protability & Identity is fragmented across enterprises & Identity can be portable across enterprises \\ 
		\hline
	\end{tabularx}
\end{table}

Centralized identity model may have single point failure in identifier management, also security issues like data leakage. With sensitive information holding on certain authorities, whether the data leakage is caused by cyber attacks or unscrupulous organizations trading user data, the users' privacy are damaged. Furthermore, having a recognizable and portable identifier is important, otherwise, it is hard to cooperate fragmented identities of different data formats among institutions, and organizations may not approve identifiers of others.

%here, todo
In the decentralized identity model, the digital footprints of entities is made up of Verifiable Credential (VC) issued by trusted issuer, such as school and government, and VCs are only worthy when verifying party recognize the issuer. If the VC is verified, the message will be labelled as trusted. Fig. shows the relationship of VC issuer, verifier and user.

In our architecture, a decentralized self-sovereign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority. TangleID is built on top of MAM where change logs of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable. The identity information such as public key, unique identifiers of services and metadata consists a DID document. One can easily prove himself by sharing the identifier on MAM without any authority.

>>>>

\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{float}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic,algorithm}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\graphicspath{{./images/}}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

% alternative solution => IPFS(data) + MAM(index)
\subsection{Digital Identity}
The digital identity represents an entity and holds the digital assets within the digital world, it is important to prove and show the identity to others during interactions. In our architecture, a self-sovereign identity system TangleID\cite{TangleID} is used to manage the identity information that allow entities to prove its identity without any third-party authority. TangleID is built on top of MAM where change logs of the Decentralized Identifiers (DIDs)\cite{DID} defined by W3C is traceable. The identity information such as public key, unique identifiers of services and metadata consists a DID document. One can easily prove himself by sharing the identifier on MAM without any authority.
